Title Goes Here

### 2020-05-01 analysis/paper/paper.Rmd
add set seed

We are also interested in whether there is a variation in topic choices between these two genders in archaeological conferences. To do this we have used topic modeling, which is a method to automatically find related groups of words that resemble 'themes' or 'topics'. We used Latent Dirichlet allocation (LDA) because LDA does not treat one topic, which consists of many words, as separate from another topic. That is, a word can be present in many topics but with differnt weightings. When using LDA, we have to first decide on the number of topics that the method will identify in our texts. We used the R package ldatuning (Nikita 2020) to compute an optimal number of topics for the LDA method to identify. We then create a topic model for all our texts, this will assign all words in every document into our set number of topics, and assign each word a probability based on its per-topic-per-word probability. To visualise the topic model we use the top 10 words within each topic as keywords to represent each topic. We excluded words that are common in the field of archaeology or have little semantic value, for example, 'the', 'a', 'el', 'al', 'archaeology', etc. We generated one topic model per conference. Each presentation at each conference is then assigned a vector of topic probabilities.

@@

# Results

>>>>

We are also interested in whether there is a variation in topic choices between these two genders in archaeological conferences. To do this we have used topic modeling, which is a method to automatically find related groups of words that resemble 'themes' or 'topics'. This approach does not treat one topic, which consists of many words, as separate from another topic. That is, a word can be present in many topics but with differs weightings. When generating topic models, we have to first decide on the number of topics that the method will identify in our texts. We then create a topic model for all our texts, this will assign all words in every document into our set number of topics, and assign each word a probability based on its per-topic-per-word probability. To visualise the topic model we use the top 10 words within each topic as keywords to represent each topic. We excluded words that are common in the field of archaeology or have little semantic value, for example, 'the', 'a', 'el', 'al', 'archaeology', etc. We generated one topic model per conference. Each presentation at each conference is then assigned a vector of topic probabilities.

@@

# Results
```{r}
number_of_papers_saa_2018 <-  ...
```

- some basic details ( 1 para)
-- number of papers that are in our sample for each conference
-- number of men and women first-named presented, state the gender ratio 
-- number of people that we could not assign a gender to

The number of ... `r number_of_papers_saa_2018` ...

- the main details
-- number of topics that are optimum for each conf (1 para)
-- variance of topics with gender for each conf (1 para)
